---
title: "Assignment 2"
author: "Name (Roll No.)"
date: '2022-07-01'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Assignment 2

## Langauge Model

Q1. Find five different speeches from your favorite political leaders (from any source). For potential sources, speeches by prime ministers of India see https://eparlib.nic.in/handle/123456789/800962 (you can ignore question answers). You may choose speech by other member of parliament from the same source. Ensure that all texts are a minimum of 500 words and are from same person. 
a. Build 1-3gram model based on these speeches. Fine tune it for values of D1, D2 and D3 for mkn smoother. 
b. Predict the most probable word after "India" from the vocabulary of the person.
c. Select the best ngram model and produce 10 sentences from the model.

Hint: largely follow ngram (where I used sherlock data) code.




## Image processing

Click a pic of you iimb identity card, read the image in R and extract as many information you can from the image (Name, Roll NO, DOB, Blood Group, your pic(optional)).


```{r pressure, echo=FALSE}
# add chunks from pan scan rcode
```



Select any image and read it in R. Play with differnt convolution matrix (create 3 different convolution matrix of size 5X5, explain the ouput.). Write one big matrix to flip the image (matrix could be as large as image size itself).


```{r pressure, echo=FALSE}
# add chunks from pan scan rcode
```

